---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# ScoreCaddie

ScoreCaddie is made to give you simple to use tools for looking at golf performance data. It lets people figure out important statistics like driving accuracy, greens in regulation, scoring averages, and putting performance. The package also has features that let you keep track of score trends over several rounds and figure out a simplified handicap index. All of the functions are easy to use and accept numeric vectors, which makes it easy for golfers to check their progress and make improvements.


## Functions

- `score_avg()`: Calculates average golf score
- `driving_accuracy()`: Calculates fairway accuracy percentage
- `gir_rate()`: Calculates greens in regulation percentage
- `putt_efficiency()`: Summarizes putting performance
- `round_trend()`: Tracks score trends over multiple rounds
- `handicap_index()`: Generates a simplified golf handicap

## Example

```{r}
devtools::load_all()

score_avg(c(72, 78, 81))
driving_accuracy(c(10, 9, 11), c(14, 14, 14))
gir_rate(c(8, 10, 9), c(18, 18, 18))
putt_efficiency(c(30, 32, 28))
round_trend(1:3, c(72, 74, 70))
handicap_index(c(95, 92, 88, 85, 90))
